\addcontentsline{toc}{chapter}{Acknowledgements}
\chapter*{Acknowledgements}
I wish to sincerely thank all those who assisted me in achieving this monumental task.

\vspace{1em}
Firstly, I acknowledge the time, effort, knowledge, and (most importantly) patience given to me by my supervisors: Dr Drew Allen\footnote{\label{MQ}\ Macquarie University, Australia} for his foresight in experimental design and statistical finesse, and Dr Hendrik Poorter\footnote{\label{Julich}\ Forschungszentrum Jülich, Germany} for his expert knowledge on botanical experimentation and his academic guidance.

\vspace{1em}
I extend my thanks and appreciation to Dr Muhammad Masood\footnoteref{MQ} for his expert management of the Plant Growth Facility at Macquarie University where my glasshouse experiments were carried out. His diligence and assitance made what would have been a very stressful time a breeze.

\vspace{1em}
I also wish to thank Dr Ajay Narendra\footnoteref{MQ} and Dr Matthew Kosnik\footnoteref{MQ} for their management of the MRes programme at Macquarie University. Their knowledge of how to navigate through the tedious administrative tasks are greatly appreciated.

\vspace{1em}
Finally, but not at all least, I fondly extend my gratitute to two particular members of my fellow cohort who helped me in more ways than they know: Paige Lieurance\footnoteref{MQ} for her assistance with my glasshouse experiments, and Keira Chrystal\footnoteref{MQ} for her emotional support and level-headed accountability. And each again for their dear friendship.

\vspace{2em}
\begin{center}
  \Large
  \textbf{\textit{Ad maiorem Dei gloriam}}
\end{center}
